---
title: "Validation results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet = TRUE)
library(targets)
library(tidyverse)
```

This report contains the validation results of a small Bayesian model. Here, we summarize the results computed in earlier targets of the pipeline. We reference our targets with `tar_load()` and `tar_read()`. This ensures

1. Because of the `tar_render()` function from the [`tarchetypes`](https://wlandau.github.io/tarchetypes) package (see `_targets.R`) `targets` automatically detects the dependencies of this report and rebuilds it when its dependencies change.
1. We can run the report by itself if the targets are already in the `_targets/` data store.

## Continuous covariate

The targets created by [`tar_stan_mcmc_rep_summary()`](https://wlandau.github.io/stantargets/reference/tar_stan_mcmc_rep_summary.html) give us a data frame with one row per parameter per simulated dataset and columns with information about our fitted models.

```{r, paged.print = FALSE}
tar_read(continuous)
```

If we implemented the model in `stan/model.stan` correctly, then roughly 90% of our posterior intervals should cover the true parameters of interest.

```{r}
tar_read(cover_continuous)
```

Likewise for the model runs with the discrete covariate.

```{r}
tar_read(cover_discrete)
```
